Javelins with hyper3 objects

### 2022-04-19 inst/javelin.Rmd
slight improvements

Above we see that Chopra threw the longest and second-longest throws
of 87.58m and 87.03 respectively; Vadlejch threw the third-longest
throw of 86.67m, and so on.  It is easy to plot the data in visual
form:

@@

```{r,plotm}
rbind(one=m1,two=m2)
pie(m1)
pie(m2)
dotchart(m1,pch=16)
dotchart(m2,pch=16)
par(pty="s")
plot(m1,m2,pch=16,type="p",asp=1)
abline(0,1)
```

>>>>

Above we see that Chopra threw the longest and second-longest throws
of 87.58m and 87.03 respectively; Vadlejch threw the third-longest
throw of 86.67m, and so on.  `NA` entries correspond to no-throws.  It
is easy to plot the data in visual form:

@@

```{r,plotm}
rbind(one=m1,two=m2)
pie(m1)
pie(m2)
dotchart(m1,pch=16)
dotchart(m2,pch=16)
abline(0,1)
ordertransplot(m1,m2)
```
